A neural coarse graining theory of consciousness

### 2018-11-08 Paper_neural_coarse_graining_of_consciousness.tex
Update from local

		\subsection{Biological Creature may try to achieve closure even the environment is not \ideaCallout{Maybe not necessary}}

@@

		Nevertheless, to achieve information closure (so as NTIC) in highly stochastic systems (e.g., the neural system) is challenging. The current states of the system have low predictability of its future states due to the stochasticity. Information processing in the neural system is suffered from multiple noise sources throughout, including sensory, cellular, electrical, and synaptic noises. Previous studies have shown that states of neurons have large trial-to-trial variability at the cellular level. That is, the same pattern of activity never occurs twice even when the same stimulus is presented. Neurons are inevitably subject to thermal fluctuations and other physical noises \citep{faisal2008noise}. Furthermore, environmental information is always only partial observable to individual sensors and neurons which only receive little amount of information from the environment. Therefore, self and environmental predictive information is difficult to be represented at the cellular level. It is implausible to construct NTIC processes at this level.

		However, to overcome the difficulty, the neural system to achieve NTIC through coarse-graining.

@@

			@ It is important to note that NTIC should not be a monotonic function of scale of coarse-graining. For the extreme case xxxxx

@@

			@ \rewrite{
				neurons are noisy: the same pattern of activity never occurs twice, even when the same stimulus is presented.}

			%% Partial observable 
			@ And every individual sensor only receives a little amount of information about the environment.

>>>>

		\subsection{Biological Creature may try to achieve closure even the environment is not \ideaCallout{Maybe not necessary}}1

@@

		%% stochasticity at microscopic levels
		Nevertheless, to achieve information closure (so as NTIC) in highly stochastic systems (e.g., the neural system) is challenging. The current states of the system have low predictability of its future states due to the stochasticity. Information processing in the neural system is suffered from multiple noise sources throughout, including sensory, cellular, electrical, and synaptic noises. Previous studies have shown that states of neurons have large trial-to-trial variability at the cellular level. That is, the same pattern of activity never occurs twice even when the same stimulus is presented. Neurons are inevitably subject to thermal fluctuations and other physical noises \citep{faisal2008noise}. Furthermore, environmental information is always only partial observable to individual sensors and neurons which only receive little amount of information from the environment. Therefore, self and environmental predictive information is difficult to be represented at the cellular level. It is implausible to construct NTIC processes at microscopic levels.

		%% encoding information via coarse-graining
		However, to overcome the difficulty, one way to encode a stable information in neural system is to encode information in coarse-grained variables. Coarse-graining here is referred to many-to-one functions that map microscopic states to macroscopic states.\needref{Do we need reference?}

		%% Our argument

		%% not monotonic
		It is important to note that NTIC should not be a monotonic function of scale of coarse-graining. Overly coarse-graining system states can lead to low degrees of NTIC. For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have enough information capacity and thus losses  the self and environmental predictive power. This notion is also supported by empirical evidence. \cite{sederberg2018learning} showed that the efficiency of reading out  self-predictive information of neural population is higher when cell number in populations is 4 than 7 and 10-cell sets. This implies an optimal coarse-graining scale for NTIC processes. % Perhaps the best way to combine more than four cells is to break down the readout into indivisible units of four cells, which are later recombined in subsequent processing.}\citep{sederberg2018learning}

@@

@@
